The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex

\subsection*{Some background and notation}  For most of this article, we work in a polynomial ring over a finite field of  characteristic $p>0$.  Unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in this ambient ring.  The ideal of this ring generated by the ring's variables is denoted $\idealm$.

Let us roughly outline how many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).   Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as $e \to \infty$.

@@

There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
\begin{itemize}
\item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
\item \autoref{sec.IsFPT} explains the package's functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
\item \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
\end{itemize}

This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.

\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
Our package coauthors are (LIST NAMES), and others who contributed code are (LIST OTHER NAMES). %Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker. 
We are also grateful the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016. 
We are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its support for the Coding Sprint \emph{F-thresholds in Macaulay2} in 2019, where the current version of the package was finalized and this paper was completed.

\newpage

>>>>

\subsection*{Some background and notation}  
The functionality implemented in the \emph{FrobeniusThresholds} is not restricted to nonsingular ambient rings (see Section \ref{sec.IsFPT}).
However, for most of this article, we work in a polynomial ring over a finite field of  characteristic $p>0$, and we remain in this case throughout the introduction for the sake of clarity.  
Unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in such a ring.  The ideal of this ring generated by the ring's variables is denoted $\idealm$.

Let us roughly outline the way in which many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).   Finally, normalize this integer by dividing by some power of $p^e$, and take the limit as $e$ approaches infinity.

@@

There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
\begin{itemize}
\item \autoref{sec.Nu} describes the methods for approximating the $F$-pure threshold and other $F$-thresholds.  
\item \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
\item \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
\end{itemize}
This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.

\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
Our package coauthors are Dan Smolkin (LIST MORE NAMES), and Zhibek Kadyrsizova, Moty Katzman (LIST MORE NAMES) contributed valuable code to the package. 
%Erin Bela, Juliette Bruce, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Matthew Mastroeni

Many thanks go to the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.

Finally, we are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its generous support for our 2019 Coding Sprint. 
The current version of the package was finalized during these events.
